---
title: "Daily Service Reliability Report"
author: "Mike Nugent, Jr."
date: '`r gsub(" 0"," ", format(Sys.Date(), "%B %d, %Y"))`'
knit: (function(inputFile, encoding){rmarkdown::render(inputFile,encoding = encoding,output_file = paste0(format(Sys.Date(), "%Y%m%d"), " Service Reliability Report", '.html'))})

#paste this back in later
#"//iptc-prtsvr1/shared/Transportation Management/Service Reliability Reports")})

  
output: 
  html_document:
    df_print: paged
    fig_cap: true
    code_folding: hide
    toc: true
    toc_depth: 2
---

```{r set libraries and options, include=F}

library(data.table)
library(dplyr)
library(kableExtra)
library(scales)
library(lubridate)


knitr::opts_chunk$set(echo = TRUE,message = F)

```

```{r define date variables, include = FALSE}

#dynamic date vars
yesterday <- lubridate::floor_date(Sys.Date() - 1
                                         , unit = "day"
                                         )

#current_month_avail <- floor_date(Sys.Date() - 1,unit= "month")

since_september <- "2019-09-01"

last_month_end <- lubridate::floor_date(Sys.Date()
                                        , unit = "month"
                                        ) - 1

last_month_start <- lubridate::rollback(last_month_end
                                        , roll_to_first = TRUE
                                        , preserve_hms = FALSE
                                        )

report_start_time <- Sys.time()

yesterday_full_date <- gsub(" 0"
                            , " "
                            , format(yesterday
                                     , "%B %d, %Y" 
                                     )
                            )

last_month_name <- format(last_month_start
                          , "%B"
                          )

last_week_start <- lubridate::floor_date(Sys.Date() - 7
                                         , unit = "week"
                                         )

last_week_end <- lubridate::ceiling_date(Sys.Date() - 7
                                         , unit = "week"
                                         ) - 1


```
This report presents key service reliability metrics: on-time performance (OTP) and headway adherence. Unless otherwise noted, **this report concerns service provided on `r yesterday_full_date`**.

## OTP

Operators are considered "on-time" if while in revenue service they depart a timepoint within one minute early or five minutes late from the scheduled time of departure.

On-time performance is calculated as the number of on-time depatures divided by the total number of departures for each category (mode, operator, month, etc).

```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
options(dplyr.summarise.inform = FALSE)
```


```{r get and clean data, results='asis'}
# gather, clean, transform data

# get Avail adherence

con2 <- DBI::dbConnect(odbc::odbc()
                       , Driver = "SQL Server"
                       , Server = "AVAILDWHP01VW"
                       , Database = "DW_IndyGo"
                       , Port = 1433
                       )

  
# get calendar key
DimDate_since_september <- tbl(con2
                               , "DimDate"
                               ) %>%
  dplyr::filter(CalendarDate >= since_september
         , CalendarDate <= yesterday
         ) %>%
  dplyr::collect() %>%
  data.table(key = "DateKey")

DimDate_yesterday <- DimDate_since_september[as.IDate(CalendarDate) == as.IDate(yesterday)]

# get month to date calendar key

DimDate_last_month <- DimDate_since_september[CalendarDate >= last_month_start &
                                                CalendarDate <= last_month_end
                                              ]
  
DimDate_last_month_last_day <- max(DimDate_last_month$DateKey)

DimDate_last_month_first_day <- min(DimDate_last_month$DateKey)

# get last week calendar key

DimDate_last_week <- DimDate_since_september[CalendarDate >= last_week_start &
                                               CalendarDate <= last_week_end]
  
  
# get DimPattern

DimPattern <- dplyr::tbl(con2
                         , "DimPattern"
                         ) %>% 
  dplyr::collect() %>%
  data.table(key = "PatternKey")

# get routes

DimRoute <- dplyr::tbl(con2, "DimRoute") %>% 
  dplyr::collect() %>%
  data.table(key = "RouteKey")

# get vehicles

DimVehicle <- dplyr::tbl(con2, "DimVehicle") %>% 
  dplyr::collect() %>%
  data.table(key = "VehicleKey")

# get route 90 BRT

DimRoute_90 <- DimRoute[RouteDesc == "Red Line"]
  
# get stops

DimStop <- dplyr::tbl(con2, "DimStop") %>%
  dplyr::collect() %>%
  data.table(key = "StopKey")


# get time (for hour of day OTP)

DimTime <- dplyr::tbl(con2, "DimTime") %>% 
  dplyr::collect() %>%
  data.table(key = "TimeKey")

# get operators 

DimUser <- dplyr::tbl(con2, "DimUser") %>%
  dplyr::collect() %>%
  data.table(key = "UserKey")

# get blocks 

DimBlock <- dplyr::tbl(con2, "DimBlock") %>%
  dplyr::collect() %>% 
  data.table(key = "BlockKey")

# get trips, for direction

DimTrip <- dplyr::tbl(con2, "DimTrip") %>%
  dplyr::select(TripKey, DirectionDesc) %>%
  dplyr::collect() %>% 
  data.table(key = "TripKey")


# get data since september, and then join it

FactTimepointAdherence_since_september <- dplyr::tbl(con2
                                                     , "FactTimepointAdherence"
                                                     ) %>% 
  dplyr::select(DateKey
                , PatternKey
                , RouteKey
                , UserKey
                , DepartStopKey
                , DepartTimeVarianceSecs
                , -CoordinateList
                , -TimepointGeom
                ) %>% 
  dplyr::filter(DateKey %in% local(DimDate_since_september$DateKey)
                , !is.na(DepartTimeVarianceSecs)
                ) %>%
  dplyr::collect() %>%
  data.table()

# get Avail adherence for yesteday

FactTimepointAdherence_yesterday <- FactTimepointAdherence_since_september[DateKey == DimDate_yesterday$DateKey]
  

# join

dt_left_join <- function(x = NULL
                         , y = NULL
                         , by.x = NULL
                         , by.y = NULL
                         , column_names = NULL
                         ){
  if(is.null(column_names)){
    x[y
      , on = paste0(by.x
                    , "=="
                    , by.y
                    )
      ]
    } else {
      x[y[,.()]
        ]
    }
}

columns <- c("StopKey","StopID","StopDesc","StopReportLabel")

DimStop[,..(columns)]

FactTimepointAdherence_since_september_test <- FactTimepointAdherence_since_september[1]


FactTimepointAdherence_since_september[DimStop[,.(StopKey
                                                  , StopID
                                                  , StopDesc
                                                  , StopReportLabel
                                                  )
                                               ]
                                       ,on = c("StopKey" = "DepartStopKey")
                                       ,names(DimStop[,.(StopKey
                                                         , StopID
                                                         , StopDesc
                                                         , StopReportLabel
                                                         )
                                                      ]
                                              ) := mget(paste0("i."
                                                               , names(DimStop[, .(StopKey
                                                                                   , StopID
                                                                                   , StopDesc
                                                                                   , StopReportLabel
                                                                                   )
                                                                               ]
                                                                       )
                                                               )
                                                        )
                                       ][DimDate_since_september[]]



DimStop


FactTimepointAdherence_since_september_joined <- FactTimepointAdherence_since_september  %>%
  
  left_join(DimStop, by = c("DepartStopKey" = "StopKey")) %>%
  left_join(select(DimDate_since_september, DateKey, CalendarDate), by = "DateKey")



# set route 90 OTP

FactTimepointAdherence_90 <- FactTimepointAdherence_raw %>% 
  filter(RouteKey %in% local(DimRoute_90$RouteKey))

# join stops

FactTimepointAdherence_joined <- FactTimepointAdherence_90 %>%
  left_join(DimStop, by = c("DepartStopKey" = "StopKey")) %>%
  left_join(select(DimDate_yesterday, DateKey, CalendarDate), by = "DateKey")

# date/data check

# nrow(FactTimepointAdherence_since_september_joined)
# 
# sort(unique(FactTimepointAdherence_since_september_joined$CalendarDate))
# 
# nrow(FactTimepointAdherence_raw )

# set index for September data

FactTimepointAdherence_since_september_joined$index <- 1:nrow(FactTimepointAdherence_since_september_joined)

FactTimepointAdherence_since_september$index <- 1:nrow(FactTimepointAdherence_since_september)

```